---
title: "early_data"
author: "Charlie Olmert"
date: "10/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# downloading the relevant libraries
library(tidyverse)
library(dplyr)
library(readxl)
library(janitor)
library(knitr)
library(kableExtra)
```

For the project, I plan to download the individual and team statistics from all of last year's games for the men's varsity lacrosse team. Below, I have just downloaded the individual statistics from the first game, shown it in a table, and calculated Harvard's total shots. Going forward, I plan to rewatch our games from last year and time when shots were taken during each possession to see how we will need to adjust as NCAA lacrosse is adding a shot clock this year.
```{r echo = FALSE}
# creates a dataframe containing the individual statisitics from the UMass Lowell game
umass_stats <- read_excel("2018 Season Stats.xlsx", skip = 1, n_max = 45) %>% 
  clean_names()

# sets missing values (players who did not record a stat in the given column) equal to 0
umass_stats[is.na(umass_stats)] <- 0

umass_stats %>% 
  # saving the data to be used in Shiny app
  write_rds(path = "project_test/saved_data")

# creates a table of the data
umass_stats %>% 
  kable(caption = "Individual statistics from the game against UMass-Lowell") %>% 
  kable_styling(bootstrap_options = "striped")

# calculates and prints the total number of shots taken
umass_stats %>% 
  summarise(total_shots = sum(sh))
```

